\documentclass [11pt,fleqn]{article}

\usepackage{amssymb}
%\usepackage{epsf,psfig,graphicx}
%\usepackage{epstopdf} % TJL ADDED
\usepackage{bm}
\usepackage{epsf,graphicx}
\usepackage{psfrag}
\usepackage{amsmath}
\usepackage[mathscr]{euscript}
\usepackage{color}
\topmargin     -0.60in  % (adjusted for printer bias) 
\headheight      .00in  % (no headers) 
\headsep         .50in  % (top margin + headers + skip) 
\textheight     9.50in  % (instructions: 9 1/8'' min, 9 7/16'' max) 
\textwidth      6.00in  % 2*3.33 + .33 = 6.99 
\oddsidemargin  0.3125in  % (subtracted 1inch bias) 
\evensidemargin 0.3125in 
%\renewcommand{\baselinestretch}{1.5} 
\parindent .0in 
\parskip 10pt 


\font \bigtenrm=cmmi10 scaled\magstep2 
\def \dt {\delta\tau} 
\def \ve {\varepsilon} 
\def \ch {{\cal H}} 
\def \del {\partial} 
\def \be {\begin{equation}} 
\def \ee {\end{equation}} 
\def \beq {\begin{eqnarray}} 
\def \eeq {\end{eqnarray}} 
\def \tv {\tilde v} 
\def \veren {\varepsilon^{\rm ren}_f} 
\def \vef {\varepsilon^0_f} 
\def \su {\uparrow} 
\def \sd {\downarrow} 
\def \CR {\nonumber\\} 
\def \hfb {\hfill\break} 
\def \tb {\bar{t} } 
\def \kb {\bar{k} } 
\def \tbB {\bar{t}_B } 
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
%\def \ul{#1} {$\underline{#1 }$}

\usepackage{authblk}
\usepackage{lineno}
\title{Nanoparticle twinning observed using solution correlated x-ray scattering}
%\author[1]{ Derek Mendez }
%\author[3]{ Thomas J. Lane}
%\author[1,2]{Jongmin Sung}
%\author[7]{Jonas Sellberg}
%\author[4,6]{Cl\'ement Levard}
%\author[1]{Herschel Watkins}
%\author[7]{Aina E. Cohen}
%\author[7]{Michael Soltis}
%\author[2,5]{Shirley Sutton}
%\author[2]{James Spudich}
%\author[3]{Vijay Pande}
%\author[7]{Daniel Ratner}
%\author[1,7]{Sebastian Doniach} %\thanks{corresponding author: sxdwc@slac.stanford.edu}}

%\affil[1]{Stanford University Department of Applied Physics, Stanford, CA 94305}
%\affil[2]{Stanford University Department of Biochemistry, Stanford, CA 94305}
%\affil[3]{Stanford University Department of Chemistry, Stanford, CA 94305}
%\affil[4]{Stanford University Department of Geological and Environmental Sciences, Stanford, CA 94305}
%\affil[5]{Stanford University School of Medicine, Stanford, CA 94305}
%\affil[6]{Aix-Marseille Universit\'e, CNRS, IRD, CEREGE UM34, 13545 Aix en Provence, France}
%\affil[7]{SLAC National Accelerator Laboratory, Menlo Park, CA 94025}

%\renewcommand\Authands{ and }
\author{Doniach group}
\date{}
\begin{document} 
%\setpagewiselinenumbers
%\linenumbers
\maketitle

\delimitershortfall=-1pt

%{\bf Abstract}


%{\bf Keywords/phrases} 

\section{Introduction}

Solution correlated x-ray scattering (SCXS) is an emerging field which involves recording many snapshot exposures of a solution, and employing photon intensity correlation analysis in order to recover a function dependent only on the average internal structure of the objects in solution phase [1]. SCXS has potential to reveal the structural properties of proteins without the use of crystalization or single protein imaging. An obvious precursor to the study of soft matter SCXS is that of nanoparticles (NPs), due to their typically large scattering cross sections. NP solutions are used in chemical catalysis, and the overall shape and atomic structure of the NPs are directly related to their chemical properties [2,3]. As such, there is great need for additional characterization methods. Great work has been done describing the thermodynamics and kinetics of NP growth and formation [4,5]. It is known that smaller NPs (tens of nanometers) tend to form complicated twinning structures, e.g. icosahedral twins [6,7,8]. Previously, twinning has been observed using electron microscopy and tomography [9,10], where one images single NP projections. On the other hand, conventional powder x-ray diffraction measurements, used widely in industry to characterize ensembles of NPs, are isotropic averages and don't show signs of twinning (figure 1).
 
\section{Theory}
If the x-ray source is bright enough, then an exposed object in solution can scatter photons into at least two directions, $\bm q_1$ and $\bm q_2$. While the orientation of this object is random, the angle $\,\, \cos (\psi) = (\bm q_1 \cdot \bm q_2)/(q_1 \, q_2 )\,\,$ is not; it is constrained by the objects internal atomic structure. A crystalline NP scatters photons into discrete vectors $\bm g_{hkl}$. Let a detector be a set of pixels $\{\bm q\}$. Then an NP at orientation $\omega$ can scatter into the detector provided 

\be \label{condition}
\hat{\bm R}_\omega \cdot \bm g_{hkl} \in \{\bm q\}
\ee

where $\hat{\bm R}_\omega$ is a rotation operator. During each exposure of the solution, we assume a small fraction of NPs in solution are oriented such that condition (\ref{condition}) is met for two scattering directions, $\bm g_{hkl}$ and $\bm g_{h'k'l'}$. This double Bragg scattering produces angular intensity correlations between pixels whose angular separation corresponds to the interplanar angles between sets of crystallographic planes $hkl$ and $h'k'l'$. In a typical exposure, most NPs will not scatter into the detector, and the ones that do will not be oriented such that they scatter into multiple detectable directions. Therefore, the average exposure is comprised of a large fraction of randomly scattered photons (owing to the orientation randomness in  a solution). As such, the signal-to-noise is much less than unity for a single exposure, and scales as the square root of the number of averaged exposures, $N_s$ [12]. We consider an exposure to be a snapshot, meaning the NPs should not be moving significantly throughout the exposure duration. This is accomplished automatically with the femtosecond timescale pulses of the SACLA facility [13]. However, SCXS can be conducted at synchrotron facilities, provided  that the sample is prepared accordingly, and that it is cooled during exposure [14,15].  For example, the $\{111\}$ family of planes for face-centered-cubic NPs will produce angular correlations at

\be \label{g1}
\frac{\bm g_{111} \cdot \bm g_{11\bar{1}}}{|\bm g_{111}| |\bm g_{11\bar{1}}| } = \frac{1}{3}
\ee

and

\be \label {g2}
\frac{\bm g_{111} \cdot \bm g_{\bar{1}\bar{1}1}}{|\bm g_{111}| |\bm g_{\bar{1}\bar{1}1}| } = -\frac{1}{3}
\ee

in the $\{111\}$ Bragg ring (See figure 1A ). Note that these are supplementary angles, which is a direct consequence of Friedel symmetry [11] between $g_{11\bar{1}}$ and $g_{\bar{1}\bar{1}1}$. The $\{111\}$ planes scatter photons into a Bragg ring of constant magnitude $q_{111} = ( 2\pi ) / ( d_{111} )$ where $d_{111}$ is the spacing between (111) planes. These photons forms a Bragg ring of pixels $I(q_{111},\phi)$ on a planar detector. In order to realize the correlations (\ref{g1}, \ref{g2}), one calculates the mean auto-correlation of $\{111\}$ Bragg rings over exposures $s$

\be \label{autocorr}
C(q_{111}, q_{111}, \Delta) = \sum _s ^ {N_s} \int _0^{2\pi} I_s(q_{111}, \phi  )\, I_s(q_{111}, \phi + \Delta)\, d\phi
\ee

and projects [ref] this correlation onto the Ewald sphere using the relationship

\be
\cos( \psi) = cos( \Delta ) \, \cos ^2 ( \theta_{111} )  + \sin ^2(\theta_{111} )  
\ee

where $\theta_{111}$ is the scattering angle at wavelength $\lambda$

\be
q_{111} = \frac{ 4\pi }{\lambda } \sin (\theta_{111})  
\ee


\section{Experimental}
60 nanometer Gold NPs were purchased from Nanopartz Inc. [ref] and suspended in LCP at a concentration of 40 mg/mL. The viscous solution was injected into the beam as a constant stream using a  hamilton 7780 syringe needle with inner diameter 130 $\mu m$.

The SACLA beam was focused down to a roughly $25 − 50 \mu m ^2$ spot size, and the beam repetition rate was 30 Hz. The femto-second pulses were measured using a MPCCD 8-panel detector [ref]. Gain calibrations were provided by SACLA [ref], and dark current measurements (detector readouts with the shutter closed) were performed every $5\times 10^3$ exposures and used to adjust for electronic noise common to CCD detectors. With this setup we acquired $2\times 10^6$ exposures of gold NPs which were then processed in order to calculate (\ref{autocorr}). As previously reported, any artificial correlations associated with the experiment are detrimental, and can corrupt the calculation of (\ref {autocorr}). We model the Bragg ring of a single exposure as

\be
I_s( \phi ) = 
\ee
\section{Supplemental}
Correlated x-ray scattering (CXS) is an emerging technique that aims to extract structural information from solution scattering measurements. We define a solution as a set of identical, non-interacting objects $m$, each with an independent orientation $\omega$ relative to the x-ray beam axis, governed by the objects diffusion constant. We consider $m$ as a collection of $N_a$ atoms each with position vector 
\be
\bm r^m_j (t) = \bm R^m_\omega (t)\cdot \bm r_j + \bm T^m(t) \qquad 1 \le j \le N_a
\ee 
where $\bm R^m_\omega(t)$ is a rotation operator, $\bm T^m (t)$ is a translation operator representing the center of mass position of $m$ at time $t$, and $\bm r_j$ is the position of the $j^{th}$ atom at an arbitrarily defined initial orientation. If we were to freeze the solution at an instant in time and expose it to x-ray photons of wavelength $\lambda$, then we could measure the scattering function

\be
S(\bm q, t) = \left | \sum_m \sum_{j}^{N_a} f_j(q) \,e ^ { -i \,\bm q \cdot \bm  r^m _j (t)  } \right |^2
\ee

Here $f_j( q  )$ is the atomic form factor of the $j^{th}$ atom$, \bm q$ represents a position in reciprocal space (e.g. of a pixel) at scattering angle  

\be \label{angle}
\sin(\theta) = \frac{ \lambda }{ 4 \pi}\,q
\ee

and the outer sum is over all exposed $m$. In general, $S(\bm q, t)$ may be written as

\be \label{ sums }
S( \bm q, t) = \sum_m \left | A^m_\omega (\bm q ) \right|^2 + \sum _{ m \neq m' } A^m_\omega (\bm q) \left (A^{m'}_\omega (\bm q) \right )^*
\ee

where 

\be
A^m_\omega (\bm q) = \sum_{j}^{N_a} f_j(q) e^{ -i \,\bm q \cdot \bm  r^m_j (t)  }
\ee

The strength of the interference term on the RHS of (\ref{ sums }) depends on both the concentration of the sample, and the magnitude of the scattering angle (\ref{angle}). In what follows we will work at relatively high scattering angles, hence we can safely neglect this limit such that we have

\beq \label{ scatter}
S( \bm q, t) &=& \sum_m \left | A^m_\omega (\bm q) \right|^2 \\
&=& \sum_m \left | \sum_{j}^{N_a} f_j(q)\, e^ { -i \,\bm q \cdot \bm  r^m _j (t)} \right | ^2   \\
&=& \sum_m \left | \sum_{j}^{N_a} f_j(q)\, e^ { -i \,\bm q \cdot \left (\bm {R}^m_\omega \left(t\right)\cdot \bm r_j \,+\, \bm {T}^m\left(t\right) \right)} \right | ^2 \\
&=& \sum_m \left | \sum_{j}^{N_a} f_j(q)\, e^ { -i \,\bm q \cdot \bm {R}^m_\omega (t)\cdot \bm r_j }  \right | ^2 
\eeq

After exposing the solution for a finite time interval $\tau$, a pixel at $\bm q$ will record 

\be
n_s( \bm q ) \propto \int_{\tau} S( \bm q, t ) dt
\ee

photons, where $s$ is used to denote a unique exposure, referred to as a ÔøΩshotÔøΩ. For sufficiently long $\tau$, the number of photons scattered from objects in each orientation $\omega$ becomes a constant and $n_s(\bm q)$ approaches a well defined average value
%\be
%\int_{\tau} dt \sum_m  \xrightarrow{\tau \rightarrow \infty} \frac{N_m}{8\pi^2}\int d\omega
%\ee
%and we have
\be 
\bar n(q) \propto \int \left | A_\omega (\bm q) \right | ^2 d\omega
\ee

However, provided $\tau$ is much shorter than the characteristic diffusion time, one can measure a finite fluctuation of the scattering

\be \label{delta_s}
\delta n_s(\bm q) = n_s (\bm q) - \bar n (q )
\ee

By recording many exposure, each representing a different state of the solution frozen in time, one can construct a correlation function

\be \label{delta_cor}
C( \bm q_1, \bm q_2 ) = \sum_s^{N_s} \delta n_s( \bm q_1 )\, \delta n_s( \bm q_2 ) = \sum_s^{N_s} n_s( \bm q_1) n_s (\bm q_2 )  - \bar n( q_1) \bar n(q_2)
\ee

which contains detailed information beyond that contained in the isotropic $\bar n( q)$. To understand the information content stored in (\ref{delta_cor}), one must again consider the solution frozen in time (if $\tau$ is sufficiently small then this is a valid approximation). When the flux is such that each object scatters roughly one photon into a random direction (owing to the objects random orientation) then $C \rightarrow 0$. 

\section{References}

1. Kam Z. 1977 Determination of macromolecular structure in solution by spatial correlation of scattering fluctuations. Macromolecules 10:927–934. (doi:10.1021/ma60059a009)

2. Narayanan R and El-Sayed MA ,2005, Catalysis with Transition Metal Nanoparticles in Colloidal Solution: Nanoparticle Shape Dependence and Stability J. Phys. Chem. B, 109, 12663-12676

3. Radha Narayanan and Mostafa A. El-Sayed, Shape-Dependent Catalytic Activity of Platinum Nanoparticles in Colloidal Solution, Nano Lett., Vol. 4, No. 7, 2004

4. Marks, L. D. Modified Wulff Constructions for Twinned Particles. J. Cryst. Growth 1983, 61, 556−566.

5. Ringe E dx.doi.org/10.1021/jp401566m | J. Phys. Chem. C 2013, 117, 15859−15870

6. Stepwise Evolution of Spherical Seeds into 20-Fold Twinned Icosahedra Mark R. Langille et al. Science 337, 954 (2012); DOI: 10.1126/science.1225653

7. C.Y. YANG Journal of Crystal Growth 47 (1979) 274—282

8. C.Y.YANG, M.J.YACAMAN K.HEINEMANN Journal of Crystal Growth 47 (1979) 283—290

9. Marks, L. D.; Smith, D. J. High-Resolution Studies of Small Particles of Gold and Silver 0.1. Multiply-Twinned Particles. J. Cryst. Growth 1981, 54, 425−432.

10. Chien-Chun Chen et al Nature 496, 74–77 (04 April 2013) doi:10.1038/nature12009

11. Friedel G (1913) Sur les symetries cristallines que peut reveler la diffraction des rayons Rontgen. Comptes Rendus hebdo-madaires de l’Academie des Sciences 157:1533–1536

12. Kirian RA,Schmidt KE,Wang X,Doak RB,Spence JCH. 2011 Signal, noise, and resolution in correlated fluctuations from snapshot small-angle X-ray scattering . Phys. Rev. E 84, 011921. (doi:10.1103/PhysRevE.84.011921)

13. Neutze R,Wouts R,van der Spoel D,Weckert E,Hajdu J. 2000 Potential for biomolecular imaging with femtosecond X-ray pulses. Nature 406, 752–757. (doi:10.1038/35021099)


14. Kam Z,Koch MH,Bordas J. 1981 Fluctuation X-ray scattering from biological particles in frozen solution by using synchrotron radiation. Proc. Natl Acad. Sci. USA 78, 3559–3562. (doi:10.1073/pnas.78.6.3559)

15. Mendez et al, 2014,  Observation of correlated X-ray scattering at atomic resolution, Phil Trans R Soc B 369: 20130315


\end{document}






